\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2018-01-12 eg6-letters/NIM/review-1/review-1.tex
Updating comments for review

\item In my opinion, this chapter should highlight better which are the 
   improvements w.r.t. BoNuS detector to underline the originality of this 
   work. For example, better acceptance? Higher gain? Higher electric 
   stability? Lower material budget? Please quote some old and new values, 
   maybe in a table, to make them evident.\\
\textcolor{blue}{The main difference is in the design of the structure, this has 
been made clearer in this chapter.}

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ The text has been modified to clarify the z position of the 
target and the RTPC with respect to CLAS sectrometer.\\}
\textcolor{red}{- Regarding the electric field in the induction gap, it was 2.8 
kV/cm in BoNuS, does anyone know our exact field in this gap?\\}
\textcolor{blue}{- The gain of such GEM configuration has been studied by 
   CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
   Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
   for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
one should not simply add gains to each other for multilayer GEM 
amplifications.  We did not evaluate precisely the overall gain in our chamber, 
so we do not have a value for our RTPC GEM system at this point.}
>>>>>>> 10849ae3d4920c417e2d8b634ec1b3e86ec0ad03

@@

\subsection*{ Chapter 3}
\item The description of the electronics looks to me a little not well 
   organized, like a collection of info from previous descriptions from ALICE 
   and BoNuS. It is a series of details, some of which not really relevant for 
   the good understanding of the work described in the paper. So, I would put 
   only some general info (the number of channels/pad, the number of time 
   samples and their width for each channel and the number of  ADC samples and 
   their width for each channel) with the reference where to find more material 
   and just write explicitly the novelties, such as the fact that the 
   acquisition rate was increased (footnote 2).\\
\textcolor{red}{Raphael, Can you check here?}

\item Also, I understand that fig. 5 comes from reference [14], updated with 
   the values of the RTPC instead of the ALICE-TPC, but it seems to me that 
   there are some parts of the picture which have to be fixed. I list them 
   here:\\
- why does it say 768 pads?\\
- why 7.6 microsec?\\
- the anode wire e grid make no sense here\\
- why L1 and L2 (trigger levels?) \\
\textcolor{red}{Raphael, Can you check here? }

>>>>

\item In my opinion, this chapter should highlight better which are the 
   improvements w.r.t. BoNuS detector to underline the originality of this 
   work. For example, better acceptance? Higher gain? Higher electric 
   stability? Lower material budget? Please quote some old and new values, 
   maybe in a table, to make them evident.\\
\textcolor{blue}{The main difference is in the design of the structure and in the
firmware of the electronics, this has been made clearer.}

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ The text has been modified to clarify the z position of the 
target and the RTPC with respect to CLAS sectrometer.\\
Regarding the electric field it is unclear what you call the induction gap. We
provide these fields for the drift region and the inter-GEM regions which we 
find most relevant. If extra information is needed, please let us know.\\}
The gain of such triple GEM configuration has been studied by 
CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
and Meth. A522(2004)93). We evaluated only the overall gain in our chamber, 
the lack of calibration of some electronics elements makes it impossible for 
us to extract a gain specific to the GEM system at this point.}

@@

\subsection*{ Chapter 3}
\item The description of the electronics looks to me a little not well 
   organized, like a collection of info from previous descriptions from ALICE 
   and BoNuS. It is a series of details, some of which not really relevant for 
   the good understanding of the work described in the paper. So, I would put 
   only some general info (the number of channels/pad, the number of time 
   samples and their width for each channel and the number of  ADC samples and 
   their width for each channel) with the reference where to find more material 
   and just write explicitly the novelties, such as the fact that the 
   acquisition rate was increased (footnote 2).\\
\textcolor{blue}{This section has been completely reworked.}

\item Also, I understand that fig. 5 comes from reference [14], updated with 
   the values of the RTPC instead of the ALICE-TPC, but it seems to me that 
   there are some parts of the picture which have to be fixed. I list them 
   here:\\
- why does it say 768 pads?\\
- why 7.6 microsec?\\
- the anode wire e grid make no sense here\\
- why L1 and L2 (trigger levels?) \\
\textcolor{blue}{Based on previous comment, we shortened the discussion and 
droped this figure. }
